---
title: "Capstone"
author: "Cassidy"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load tidyverse etc.
```{r}
library(tidyverse)
library(dplyr)
library(scales)
library(ggplot2)
```
#How many entires are predicted to have glaucoma (glaucoma = 1) ? What is the max RNFL4.mean of those predicted to have glaucoma. Compare to mean of those predicted not to have glaucoma? Is the value of  RNFL4.mean able to predict glaucoma ?
```{r}
data <- read_csv('glaucoma_data/ds_whole.csv') %>% #read csv file
 print()

data_g1 <- data %>%   #filter for glaucoma =1
  filter(glaucoma==1) 

data_g0 <- data %>%   #filter for glaucoma =0
  filter(glaucoma==0) 

count(data_g1)#glaucoma
count(data_g0)#no glaucoma

print(max(data_g1["RNFL4.mean"])) #max RNFL4.mean of those with glaucoma
print(min(data_g1["RNFL4.mean"])) #min RNFL4.mean of those with glaucoma
print(max(data_g0["RNFL4.mean"]))#max RNFL4.mean of those without glaucoma
print(min(data_g0["RNFL4.mean"]))#min RNFL4.mean of those without glaucoma

print((max(data_g0["RNFL4.mean"])-(max(data_g1["RNFL4.mean"])))) #difference between max RNFL4.mean for those with vs without glaucoma.

print((min(data_g0["RNFL4.mean"])-(min(data_g1["RNFL4.mean"])))) #difference between min RNFL4.mean for those with vs without glaucoma.
```
##Answer
297 have glaucoma 
202 do not have glaucoma
There is a difference of 52.3 between maximum RNFL4.mean of those with versus without glaucoma.
There is a difference of 42.7 between maximum RNFL4.mean of those with versus without glaucoma.
Therefore, RLFL4.mean may be a useful metric in predicting glaucoma since those with glaucoma have a lower range of scores for this metric.   


#How does the ratio between ocular_pressure and cornea thickness change with age.


```{r}
q2 <- data %>%
  mutate(ratio = (ocular_pressure / cornea_thickness)) %>% #create new column
  select(ratio, age) %>% #pull out only these #lets just look at the new column compared to age
  ggplot(aes(x = age, y = ratio)) +
  geom_point() +
  scale_y_continuous()+ 
  scale_x_binned(n.breaks = 10) #bin into 10 age groups

q2 #print

```

##Answer The graph shows that as age increases, so does the range of ratios observed.  Ages 1-40 have smaller variation in this ratio. There also seems to be a slight increased ratio associated with increased age.



REPRODUCIBILITY
Question 1 code will work for any column where an assigned value can be called on, in this case 0 or 1. 
Question 2 code is reproducible for all values that can be divided. The scaling may need to be changed for different datasets and questions. 

